\textls[-0]{\thetitle}

### 2023-03-18 metatheory2.tex
edits

%Moreover, the linkage transformer can be considered as a syntactic sugar (or
%``library functions'' in the main text) (we will show why at the end).
%Since it is a syntactic sugar, we will not consider about the linkage
%transformers during meta-theoretic reasoning.

@@

As mentioned in \cref{sec:metatheory2}, the five forms of linkage transformers can be
thought of a library of functions that are used to construct linkages from other
linkages.
In particular, their typing rules are defined in terms of the rest of the typing
rules in \TT.
Thus, linkage transformers $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ can be defined
as syntactic sugar via an \TT inductive type with constructors
%\YZ{I reinterpreted what you wrote, but this sentence doesn't sound right to me. If linkage transformers are meta-level inductive types, aren't they just part of the syntax?}\EDJreply{I think the reason that they are syntactic sugar is because they can be interpreted using FMLTT syntax(without them), it is fine either the syntactic sugar is defined via inductive type (and then interpreted), or directly interpreted. Maybe I should remove this misleading sentence? \\ What's more, the specification/definition of syntactic sugar itself, is inductive type. Because a linkage transformer looks inductive. Maybe I should directly separate the typing rules for linkage transformer as another figure to emphasize it as an inductive construction on the rest FMLTT syntax?}
$\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$, and
the syntax $\inh{h}{\ell}$ and $\sub{h}{\gm}$ can be defined by induction on
this inductive type.

>>>>

@@

As mentioned in \cref{sec:metatheory2}, the five forms of linkage transformers can be
thought of a library of functions that are used to construct linkages from other
linkages.
In particular, their typing rules are defined in terms of the rest of the typing
rules in \TT.
Thus, linkage transformers $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ can be defined
as syntactic sugar via an inductive type (in the meta\-logic) with four constructors
%\YZ{I reinterpreted what you wrote, but this sentence doesn't sound right to me. If linkage transformers are meta-level inductive types, aren't they just part of the syntax?}\EDJreply{I think the reason that they are syntactic sugar is because they can be interpreted using FMLTT syntax(without them), it is fine either the syntactic sugar is defined via inductive type (and then interpreted), or directly interpreted. Maybe I should remove this misleading sentence? \\ What's more, the specification/definition of syntactic sugar itself, is inductive type. Because a linkage transformer looks inductive. Maybe I should directly separate the typing rules for linkage transformer as another figure to emphasize it as an inductive construction on the rest FMLTT syntax?}
$\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, and $\InhNest{}{}$.
Moreover, $\inh{h}{\ell}$ and $\sub{h}{\gm}$ can be defined
as recursive functions (in the meta\-logic) by induction on this inductive type.
We will treat linkage transformers as syntactic sugar in the meta\-theoretic development
in the rest of \cref{sec:complete-fmltt}.
